Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-04-13 ch1/chapter-introduction.tex
add some prose to the introduction- Si gaps, GMTNIRS, and OCO.  prepare for astronomy section

\section{Overview}

\section{Silicon grisms for the James Webb Space Telescope NIRCam}

@@

Si grisms like those in Chapter \ref{chSPIE_2010} served as pathfinders for Si immersion echelle grating.  The precision fabrication of Si immersion gratings is more demanding than it is for Si grisms.  The heightened precision demands for immersion gratings over grisms rises from two effects.  First, grisms are operated in transmission, whereas echelles operate in reflection.  Echelles therefore require $2n/(n-1) = 2.8$ times less wavefront error to meet the same optical performance as Si grisms.  Additionally, Si echelles operate at much steeper blaze angles than Si grisms do.  For example, an R3 echelle will will be 8.8 times more sensitive to wavefront error than its grism counterpart with a blaze angle of 6.16$^\circ$.  Taking the reflection and blaze angle effects together, we see that Si immersion echelle gratings require 25 times more precision than Si grisms of the same aperture and design wavelength.

@@

The next generation of high precision near-IR spectographs employing silicon immersion gratings will push further the demands on optical performance.  The Giant Magellan Telescope Near Infrared Spectrograph (GMTNIRS) will have 5 separate spectrograph channels, each with its own custom Si immersion grating and IR focal plane array \citep{2014SPIE.9147E..22J}.  The scientific requirements drive high spectral resolution ($R\sim100,000$) for the long wavelength channels (3$-$5.4 $\mu$m).  The design calls for a Si immersion grating between 150 and 200 mm in illuminated length- larger than our existing 100 mm immersion grating substrates.  The substrates will also have to exceed 30 mm in thickness, which is larger than what our existing fabrication equipment can handle.  In Chapter \ref{ch_SiGaps}, I demonstrate a technique to directly bond patterned Si wafers to optical Si prisms, alleviating the need for patterning and processing on monolithic Si substrates.

\section{Bonded Si wafers}

\begin{itemize}
	\item Bonding wafers will make it easier to make gratings
	\item Summary of the chapter
	\item Applicability to earth-science satellites and astronomy
\end{itemize}

\section{Allers et al. sspectroscopic sample}

>>>>

@@

Si grisms like those in Chapter \ref{chSPIE_2010} served as pathfinders for Si immersion echelle gratings.  The precision fabrication of Si immersion gratings is more demanding than it is for Si grisms.  The heightened precision demands for immersion gratings over grisms rises from two effects.  First, grisms are operated in transmission, whereas echelles operate in reflection.  Echelles therefore require $2n/(n-1) = 2.8$ times less wavefront error to meet the same optical performance as Si grisms.  Additionally, Si echelles operate at much steeper blaze angles than Si grisms do.  For example, an R3 echelle will will be 8.8 times more sensitive to wavefront error than its grism counterpart with a blaze angle of 6.16$^\circ$.  Taking the reflection and blaze angle effects together, we see that Si immersion echelle gratings require 25 times more precision than Si grisms of the same aperture and design wavelength.

@@

The next generation of high precision near-IR spectographs employing silicon immersion gratings will push further the demands on optical performance.

The Giant Magellan Telescope Near Infrared Spectrograph (GMTNIRS) will have 5 separate spectrograph channels, each with its own custom Si immersion grating and IR focal plane array \citep{2014SPIE.9147E..22J}.  The scientific requirements drive high spectral resolution ($R\sim100,000$) for the long wavelength channels (3$-$5.4 $\mu$m).  The design calls for a Si immersion grating between 150 and 200 mm in illuminated length- larger than our existing 100 mm immersion grating substrates.  The substrates will also have to exceed 30 mm in thickness, which is larger than what our existing fabrication equipment can handle.

In Chapter \ref{ch_SiGaps}, I demonstrate a technique to directly bond Si wafers to optical Si prisms, alleviating the need for patterning and processing on monolithic Si substrates.

Silicon direct bonding offers flexibility in the design and development of Si optics by allowing manufacturers to combine subcomponents with a potentially lossless and mechanically stable interface. The bonding process presents challenges in meeting the requirements for optical performance because air gaps at the Si interface cause large Fresnel reflections. Even small (35 nm) gaps reduce transmission through a direct bonded Si compound optic by 4\% at $\lambda = 1.25 \; \mu$m at normal incidence. Understanding the optical effects of such gaps and evaluation of various methods for preventing or eliminating them demands that we have a method for measuring not only the two-dimensional extent of the gaps but also their axial extent.  Existing methods for studying gaps provide only poor measures of this axial extent.  We describe a bond inspection method that makes use of precision slit spectroscopy.  Using spectroscopy, we detect and measure gaps as small as 14 nm by measuring transmission as a function of wavelength. Our analysis involves modeling multiple incoherent reflections within the substrate interfaces with a wave transfer matrix, modified for intensities rather than complex amplitudes. We infer the gap axial extent and fill factor with Monte Carlo Markov Chain (MCMC) and a flexible Gaussian process noise model.  We describe the measurement and analysis techniques and demonstrate the validity of the approach by measuring bond gaps of known depths produced by microlithography.

%Spectroscopy of planets with GMTNIRS

The innovations in silicon immersion grating technology that I have pioneered center around astronomical instruments like JWST NIRCam, IGRINS, iSHELL, and GMTNIRS.  These technologies could also benefit the Earth Science community, in which remote sensing of trace gases in the Earth's atmosphere is a major priority.  In particular, a future space-based mission like the Orbiting Carbon Observatory will associate local sources and sinks of greenhouse gases.  The scientific requirements of high spatial and spectral resolution drive a ``pushbroom'' spectrograph design, with near-IR capability to detect methane.  This spectrograph design differs from those in astronomical applications because of its much larger angular slit length, and its higher groove frequency.  The innovations in direct Si$-$Si bonding and metrology described in Chapter \ref{ch_SiGaps} will facilitate the transfer of technologies between the fields of astronomy and earth science.

The lowest mass objects in nearby star forming regions now accessible to spectroscopy are in the sub-brown dwarf regime, with estimated masses comparable to the masses of extrasolar planets and bordering the threshold of opacity limited fragmentation.  We confirm and characterize, using $R\sim 2000$ near-infrared spectroscopy, 17 candidate young substellar objects in the Ophiuchus, Lupus I, and Chamaeleon II star forming regions from the Allers et al. 2006 sample.  The spectral types range from M2$-$L2.5, with extinctions of $0 < A_V < 10$.  We assign youth based on the presence of mid-IR excess and gravity sensitive spectral indices, like the triangular $H-$band continuum shape and the $\mathrm{Na\, I}$ equivalent width.  All but one source from the photometrically selected sample of 19 are confirmed as bona fide young late type objects, an exceptional confirmation rate for this type of study.  Two of the sources are known wide-separation binaries.  We explore the advantage of increased resolution over existing low resolution spectroscopy for six objects.  The objects' derived luminosities are in the range $-3.3 < \log L/L_{\odot} < -0.6$, placing the lowest luminosity candidates comfortably in the substellar or even sub brown-dwarf mass regime.
